Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd

# Data Exploration
```{r statistic summary}

# For convenience
provide_statistics <- function(data){
  data %>%
    summarise(
      Min       = min(Grade),
      Max       = max(Grade), 
      Mean      = round(mean(Grade), 2), 
      Median    = median(Grade), 
      SD        = round(sd(Grade), 2),
      Fail_rate = round(mean(Fail), 2),
      Fail_n    = sum(Fail),
      n         = n()
      )
}

>>>>

# Data Exploration

We compute summary statistics (minimum, maximum, mean, median, standard deviation, failure rate, number of failure and count) at different levels (student, course, cluster, concentration, year and course level). We save the results in the environment `Transcript Statistics`.

```{r statistic summary}

# For convenience
provide_statistics <- function(data){

  data %>%
    summarise(
      Min       = min(Grade),
      Max       = max(Grade), 
      Mean      = mean(Grade), 
      Median    = median(Grade), 
      SD        = sd(Grade),
      `Failure Rate` = mean(Fail),
      `Failure Count`    = sum(Fail),
      Count     = n()
      ) %>%
    mutate_at(
      vars(Mean, SD, `Failure Rate`),
      round,
      digits = 2
    )
